\large{McGill University | Desautels Faculty of Management}\\ \hfill \break \hfill \break \hfill \break \hfill \break \\\Large MGSC 670 - Revenue Management\\ \textbf{Group Assignment 1: Markdown Strategy}\\ \hfill \break \hfill \break

### 2023-05-16 manuscript/manuscript.tex
added julie's student id lol
changed plots resolution, saved validation result

\author{\\\\
261083570 Konstantin Volodin\\
261078897 Ying-Fang Liang\\
260658030 Emery Dittmer\\
Julie Chanzy\\\\
\hfill \break
\\\\\textbf{Instructor:} Professor Maxime Cohen\\
\hfill \break
}

@@

@@

@@

@@

>>>>

\author{\\\\
261083570 Konstantin Volodin\\
261078897 Ying-Fang Liang\\
260658030 Emery Dittmer\\
261077392 Julie Chanzy\\\\
\hfill \break
\\\\\textbf{Instructor:} Professor Maxime Cohen\\
\hfill \break
}

@@

\subsection{Random Policy}
We will first investigate a random choice policy. 
This policy represents a likely worst-case scenario, where a company has no expertise and not logic to operate with. 
The policy will arbitrarily choose the pricing policy at each time t.

Based on the random nature of the model and rules of the model, we expect a smaller distribution then the baseline mode (presented next). 
Since we cannot raise the price once lowered the cumulative probability of a 40\% discount approaches 50\% by the end of the 15 weeks, which is the highest of any choice. 
The distribution of revenue should largely follow the distribution of the 40\% off price distribution we have observed.

@@

\subsection{likelihood shared}

@@

\subsection{Reinforcement Learning}
Some artificial intelligence models rely on supervised reinforcement learning which learn as they go. 
The models are rewarded for certain actions and attempt to maximize the reward, relying on previous runs or iterations to build off of. 
These models are ideal for repeated tasks that have defined conditions. 
For example, Open Ai in 2019 demonstrated a reinforcement learning model that simulated a game of hide and seek \cite{baker2019emergent}.
We will apply reinforcement learning to this problem, where the reward function is the maximization of the revenue, and the inputs are the app itself. 
While this model offers little explanation ability since rl models are black box models, the reinforcement learning policy may perform better than previous policies.

We expect that the reinforcement learning model will have the highest revenue and the lowest revenue distribution of all models previously tested.

@@

\subsection{Policy Comparison}

\subsection{Recommended Policy}
